Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-31 R0V0.tex
Formalized first paragraph of the section and review theorem statement and proof

\begin{proof}
\todo[inline]{Continue with the proof}

	The number of cliques $p$ in the $\mathscr{G}$ can be computed using the algorithm \cite{BronKerbosch1973}. The remainder of this proof is based on Section~II of \cite{PakazadHanssonAndersenEtAl2015}.

	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the cliques of the $\mathscr{G}$, and $\mathbin{\mathtt{card}}(\mathscr{C}_k)$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$. For each index $k\in\mathbb{N}_{[1,p]}$, let the integer $\dim_k$ denote the dimension of the set $\mathbf{X}(\mathscr{C}_k)$ and define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.

@@

>>>>

\begin{proof}
	Using the Algorithm~3.1 from \cite{VandenbergheAndersen2015}, it is possible to decompose the graph $\mathscr{G}$ into the clique tree $\mathscr{T}(\mathscr{G})$. Let the integer $p>0$ be the number of nodes of $\mathscr{T}(\mathscr{G})$. The remainder of this proof is based on Section~II of \cite{PakazadHanssonAndersenEtAl2015}.

	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the nodes of $\mathscr{T}(\mathscr{G})$, and $\mathbin{\mathtt{card}}(\mathscr{C}_k)$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$. For each index $k\in\mathbb{N}_{[1,p]}$, let the integer $\dim_k$ denote the dimension of the set $\mathbf{X}(\mathscr{C}_k)$ and define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.

@@

Note that if a graph is not chordal, it is possible to make it chordal by adding edges to the graph. The obtained graph is said to be a \emph{chordal embedding}. The above procedure can be applied for the chordal embedded graphs.
